Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2025-02-20 paper.tex
Add ref to Clamond & Dutykh

\begin{equation}
\label{eq:w_L}
W =
\frac{\partial \phi}{\partial z} =
a_L \omega_L e^{k_L z} \sin{\psi} + \mathcal{O}(\varepsilon_L^4)
\end{equation}
Evaluating these velocities at the wave surface $z = \eta_L$ rather than at
the mean water level $z=0$ is a departure from the linear theory, making the
treatment of the long waves here as weakly nonlinear.
As \citet{zhang1990evolution} point out, this is appropriate to do when the
amplitude of the long waves is of the similar magnitude or larger than the
wavelength of the short waves.

(\ref{eq:wavenumber})-(\ref{eq:wave_action2}) are the governing equations used
in this paper, with (\ref{eq:U_L})-(\ref{eq:w_L}) describing the long-wave
induced ambient velocity forcing for the short waves. 
Rather than deriving the modulation solution from the velocity
potential of two waves, as \citet{longuet1960changes} did, starting from the
crest-action conservation balances allows for a simpler derivation.

@@

>>>>

\begin{equation}
\label{eq:W_L}
W =
\frac{\partial \phi}{\partial z} =
a_L \omega_L e^{k_L z} \sin{\psi} + \mathcal{O}(\varepsilon_L^4)
\end{equation}
Evaluating these velocities at the wave surface $z = \eta_L$ rather than at
the mean water level $z=0$ is a departure from the linear theory, making the
treatment of the long waves here as weakly nonlinear.
As \citet{zhang1990evolution} point out, this is appropriate to do when the
amplitude of the long waves is of the similar magnitude or larger than the
wavelength of the short waves.

(\ref{eq:wavenumber})-(\ref{eq:wave_action2}) are the governing equations used
in this paper, with (\ref{eq:U_L})-(\ref{eq:W_L}) describing the long-wave
induced ambient velocity forcing for the short waves. 
Rather than deriving the modulation solution from the velocity
potential of two waves, as \citet{longuet1960changes} did, starting from the
crest-action conservation balances allows for a simpler derivation.

@@

The long-wave induced velocities (\ref{eq:phi})-(\ref{eq:W_L}) are accurate to
$\mathcal{O}(\varepsilon_L^3)$ when evaluated at the mean water level.
However, in this paper we depart from the mean water level and evaluate the
velocities at the surface of the long wave.
This introduces an additional error at the order of $\mathcal{O}(\varepsilon_L^2)$.
To quantify this error exactly, we compare the velocities evaluated at the
surface for a linear (small-amplitude) wave and a third-order Stokes wave,
with the surface velocity of a fully nonlinear wave.
The nonlinear wave surface velocity is calculated numerically using the method
by \citet{clamond2018accurate}.
